EasyMerge - A New Tool for Code Clones Refactoring

### 2014-03-17 paper/paper.tex
paper updates

User can click each item in the ``Possible Merges" list. When one item is selected, a corresponding clone set will be loaded. All files
associated with the set are displayed in ``Source Code Browser" tabs on the right side of the UI.
Inside the source code browser, code fragment that

@@

\section{Experimental Results}

>>>>

User can click each item in the ``Possible Merges" list. When one item is selected, a corresponding clone set will be loaded. All files
associated with the set are displayed in ``Source Code Browser" tabs on the right side of the UI, where we can navigate to the
corresponding source file by clicking each tab.
Inside the source code browser, code that will be removed after merging is between ``\#\#\#REMOVE\_CODE\_BELOW\#\#\#"
and ``\#\#\#REMOVE\_CODE\_ABOVE\#\#\#". And the replacement code is between ``\#\#\#REPLACE\_WITH\#\#\#"
and ``\#\#\#REPLACE\_END\#\#\#".

On the bottom part of the screen, the ``Log" and ``Evaluation" windows are placed on the left. The ``Log" window keeps track of
program running and debugging information. Moreover, its content will also be dumped to ``log.txt" file in EasyMerge's main folder for
book keeping purpose and developers may use it to help with writing change log. The ``Evaluation" window displays evaluation metrics
for each code clone set, and will tell user whether we recommend a code merge for the set or not.

Last but not least, the ``Extracted Method" box display the extracted method we generated as a helper function all code replacement 
in original source code files are calling. After reviewing all information and recommendation we provide, a user can perform the code refactoring for
a certain set by clicking ``Merge" button on bottom left. 
EasyMerge in turn will rewrite the source files and move the generated helper to our specific accessible file in back-end.
And all merging done in current session can be redone by clicking ``Unmerge" button if
the user performed an unwanted merge.

@@

\section{Experimental Results}
All experiments are done on a desktop computer. The testing machine has an AMD FX 3.5GHz 6 cores CPU, 16 GB of memory,
128 KB L1 cache, 6 MB L2 cache (1 MB per core), and 8 MB shared L3 cache. The machine runs Ubuntu Desktop 12.04, Python
2.7.5 and has all related packages installed. For test cases, we have three popular Python powered open source projects found on GitHub of different sizes and covers
different usage domains.
They are ``Beets - the media library management system for obsessive-compulsive music geeks", ``Fig - fast, isolated development environments using Docker",
and ``Wagtail - a new Django content management system".
